Fifteen years of decentralization attempts

### 2014-03-20 paper.tex
Problem with decentralizing fixes

	There are advantages when using a centralized authority: this authority can be used for bootstrapping, key management and to manage the reputation of the users. When removing this central authority, these components needs to be spread across the peers in the network. In this section we will explain the various problems that are involved when decentralizing Tor. In the next section, we will explain several decentralized peer-to-peer networks and make a comparison between them.

>>>>

	There are advantages to using a centralized authority: this authority can be used for bootstrapping, key management and to manage the reputation of the users. When removing this central authority, these components needs to be spread across the peers in the network. In this section we will explain the various problems that are involved when decentralizing Tor. In the next section, we will explain several decentralized peer-to-peer networks and make a comparison between them.
